### 2014-10-01 Paper_v1.tex
Updated material and methods

The control term $v_{j}$ depended upon the combination of factors which influenced the activity of enzyme $i$.
For each enzyme, we used a rule-based approach to select from competing control factors (Fig. \ref{fig-control-schematic}). 
If an enzyme was activated by $m$ metabolites, we modeled this activation as:
\begin{equation}
	v_{j} = \max\left(f_{1j}\left(\mathcal{Z}\right),\hdots,f_{mj}\left(\mathcal{Z}\right)\right)
\end{equation}where $0\leq f_{ij}\left(\mathcal{Z}\right)\leq 1$ was a regulatory transfer function that calculated the influence of metabolite $i$ on the activity of enzyme $j$. 
Conversely, if enzyme activity was inhibited by a $m$ metabolites, we modeling this inhibition as:
\begin{equation}
	v_{j} = 1 - \max\left(f_{1j}\left(\mathcal{Z}\right),\hdots,f_{mj}\left(\mathcal{Z}\right)\right)
\end{equation}Lastly, if an enzyme had both $m$ activating and $n$ inhibitory factors, we modeled the regulatory term as:
\begin{equation}
	v_{j} = \min\left(u_{j},d_{j}\right)
\end{equation}where:
\begin{eqnarray}
	u_{j} &=& \max_{j^{+}}\left(f_{1j}\left(\mathcal{Z}\right),\hdots,f_{mj}\left(\mathcal{Z}\right)\right) \\
	d_{j} &=& 1 - \max_{j^{-}}\left(f_{1j}\left(\mathcal{Z}\right),\hdots,f_{nj}\left(\mathcal{Z}\right)\right)
\end{eqnarray}
The quantities $j^{+}$ and $j^{-}$ denoted the sets of activating and inhibitory factors for enzyme $j$. 
If an enzyme had no allosteric factors, we set $v_{j} = 1$.
There are many possible functional forms for $0\leq f_{ij}\left(\mathcal{Z}\right)\leq 1$. 
However, in this study, each individual transfer function took the form:
\begin{equation}\label{eqn:control-factor}
	f_{i}\left(\mathbf{x}\right) = \frac{\kappa_{ij}^{\eta}\mathcal{Z}_{j}^{\eta}}{1 + \kappa_{ij}^{\eta}\mathcal{Z}_{j}^{\eta}}
\end{equation}where $\mathcal{Z}_{j}$ denotes the abundance of the $j$ factor (e.g., metabolite abundance), and $\kappa_{ij}$ and $\eta$ are control parameters. 
The $\kappa_{ij}$ parameter was species gain parameter, while $\eta$ was a cooperativity parameter (similar to a Hill coefficient).
The model equations were encoded using the Python programming language and solved using the ODEINT routine of the SciPy module \citep{SCIPY}.

>>>>

The control term $v_{j}$ depended upon the combination of factors which influenced the activity of enzyme $i$.
For each enzyme, we used a rule-based approach to select from competing control factors (Fig. \ref{fig-control-schematic}). 
If an enzyme was activated by $m$ metabolites, we modeled this activation as:
\begin{equation}
	v_{j} = \max\left(f_{1j}\left(\mathcal{Z}\right),\hdots,f_{mj}\left(\mathcal{Z}\right)\right)
\end{equation}where $0\leq f_{ij}\left(\mathcal{Z}\right)\leq 1$ was a regulatory transfer function that calculated the influence of metabolite $i$ on the activity of enzyme $j$. 
Conversely, if enzyme activity was inhibited by a $m$ metabolites, we modeling this inhibition as:
\begin{equation}
	v_{j} = 1 - \max\left(f_{1j}\left(\mathcal{Z}\right),\hdots,f_{mj}\left(\mathcal{Z}\right)\right)
\end{equation}Lastly, if an enzyme had both $m$ activating and $n$ inhibitory factors, we modeled the regulatory term as:
\begin{equation}
	v_{j} = \min\left(u_{j},d_{j}\right)
\end{equation}where:
\begin{eqnarray}
	u_{j} &=& \max_{j^{+}}\left(f_{1j}\left(\mathcal{Z}\right),\hdots,f_{mj}\left(\mathcal{Z}\right)\right) \\
	d_{j} &=& 1 - \max_{j^{-}}\left(f_{1j}\left(\mathcal{Z}\right),\hdots,f_{nj}\left(\mathcal{Z}\right)\right)
\end{eqnarray}
The quantities $j^{+}$ and $j^{-}$ denoted the sets of activating and inhibitory factors for enzyme $j$. 
If a process has no modifying factors, we set $v_{j} = 1$.
There are many possible functional forms for $0\leq f_{ij}\left(\mathcal{Z}\right)\leq 1$. 
However, in this study, each individual transfer function took the form:
\begin{equation}\label{eqn:control-factor}
	f_{i}\left(\mathbf{x}\right) = \frac{\kappa_{ij}^{\eta}\mathcal{Z}_{j}^{\eta}}{1 + \kappa_{ij}^{\eta}\mathcal{Z}_{j}^{\eta}}
\end{equation}where $\mathcal{Z}_{j}$ denotes the abundance of the $j$ factor (e.g., metabolite abundance), and $\kappa_{ij}$ and $\eta$ are control parameters. 
The $\kappa_{ij}$ parameter was species gain parameter, while $\eta$ was a cooperativity parameter (similar to a Hill coefficient).
Applying the general framework to the reduced coagulation network resulted in five ordinary differential equations:
\begin{eqnarray}
	\frac{dx_{1}}{dt} & =& -\left(r_{init}v_{init} + r_{amp}v_{amp}\right)\\
	\frac{dx_{2}}{dt} &=& r_{amp}v_{amp} + r_{init}v_{init} - \left(r_{inh,ATIII}v_{inh,ATIII} + r_{inh,APC}v_{inh,APC}\right)\\
	\frac{dx_{3}}{dt} &=& -r_{apc}v_{apc} \\
	\frac{dx_{4}}{dt} &=& r_{apc}v_{apc} \\
	\frac{dx_{5}}{dt} & = & -r_{inh,ATIII}v_{inh,ATIII}
\end{eqnarray}where $\mathbf{x} = \left(fII,FIIa,PC,APC,ATIII\right)^{T}$.
The model equations were encoded using the Python programming language and solved using the ODEINT routine of the SciPy module \citep{SCIPY}.
